Analysis of Monte Carlo accelerated iterative methods for sparse linear systems \tnoteref{ornl-cr}

### 2016-02-03 manuscript1/paper.tex
Added acknowledgement.

%opening
\title{Analysis of Monte Carlo accelerated iterative methods for
sparse linear systems}
\author{Michele Benzi\thanks{Department of Mathematics and Computer
Science, Emory University, Atlanta, Georgia 30322, USA
(benzi@mathcs.emory.edu). The work of this author was supported
by Department of Energy (Office of Science) grant ERKJ247.}
\and
Thomas M.~Evans\thanks{Oak Ridge National Laboratory, 1 Bethel Valley Rd., 
Oak Ridge, TN 37831, USA (evanstm@ornl.gov).}
\and Steven P. Hamilton\thanks{Oak Ridge National Laboratory, 
1 Bethel Valley Rd., Oak Ridge, TN 37831, USA (hamiltonsp@ornl.gov).}
\and 
\linebreak Massimiliano Lupo  Pasini\thanks{Department of Mathematics and Computer
Science, Emory University, Atlanta, Georgia 30322, USA (mlupopa@emory.edu).}
\and 
Stuart R.~Slattery\thanks{Oak Ridge National Laboratory,
1 Bethel Valley Rd., Oak Ridge, TN 37831, USA (slatterysr@ornl.gov).}
}
\date{}

>>>>

%opening
\title{Analysis of Monte Carlo accelerated iterative methods for
sparse linear systems \tnoteref{ornl-cr}}
\author{Michele Benzi\thanks{Department of Mathematics and Computer
Science, Emory University, Atlanta, Georgia 30322, USA
(benzi@mathcs.emory.edu). The work of this author was supported
by Department of Energy (Office of Science) grant ERKJ247.}
\and
Thomas M.~Evans\thanks{Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
Oak Ridge, TN 37831, USA (evanstm@ornl.gov).}
\and Steven P. Hamilton\thanks{Oak Ridge National Laboratory,
1 Bethel Valley Rd., Oak Ridge, TN 37831, USA (hamiltonsp@ornl.gov).}
\and
\linebreak Massimiliano Lupo  Pasini\thanks{Department of Mathematics and Computer
Science, Emory University, Atlanta, Georgia 30322, USA (mlupopa@emory.edu).}
\and
Stuart R.~Slattery\thanks{Oak Ridge National Laboratory,
1 Bethel Valley Rd., Oak Ridge, TN 37831, USA (slatterysr@ornl.gov).}
}
\tnotetext[ornl-cr]{Notice: This manuscript
  has been authored by UT-Battelle, LLC, under contract DE-AC05-00OR22725
  with the U.S. Department of Energy. The United States Government retains
  and the publisher, by accepting the article for publication, acknowledges
  that the United States Government retains a non-exclusive, paid-up,
  irrevocable, world-wide license to publish or reproduce the published form
  of this manuscript, or allow others to do so, for United States Government
  purposes.}
\date{}
